Slitasje og kjørespor

### 2023-01-31 DRAFT_slitasje.Rmd
bug: Rename and fix color palette

> *ANO could harmonie better with the Naturetype data set if it included
> 7SE and 7TK for Naturally open and Semi natural ecosystem.*

@@

It appears the proportion of each circle that is made up of the dominant
ecosystem was only recorded after year 2019. In fact, the main ecosystem
was not recorded at all in 2019:

@@

This rather dense figure needs to be looked at carefully. In the top row
we see that the sample size (number of polygons) varies between
ecosystems. For naturally open ecosystems many polygons are from high
infrastructure areas, not surprisingly, and there are few points for the
lowest impact class (zero such polygons in *Sørlandet* for example). We
may therefore not be able to extrapolate indicator values for Naturally
open areas in in *Sørlandet* with low levels of infrastructure. We can
also from the middle row see the association between the indicator
values (area weighted means) and the modified infrastructure index
(HIF). We should then not put too much weight on the bars were there is
little data (low n) and/or high standard error (sd, bottom row). For
example, with Naturally open ecosystems, Midt-Norge has the overall
lowest errors, and there we also see the kind of relationship between
the indicator and the pressure that we want to see (middle row). The
pattern is repeated for all regions except Østlandet, but there we also
see that HIF class 3 has very little data, and a high sd, and this could
explain the discrepancy (but it doesn't support the general relationship
either).

@@

```{r, fig.cap="Slitasje indicator extrapolated over Trondheim"}
tmap_arrange(
tm_shape(wetlands_slitasje_extr_trd)+
  tm_polygons(col = "w_mean",
    title="Slitasje indicator",
    palette = "viridis",
    style="cont",
    breaks = c(0,1))+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="blue")+
  tm_layout(title = "Wetland"),

tm_shape(seminat_slitasje_extr_trd)+
  tm_polygons(col = "w_mean",
    title="Slitasje indicator",
    palette = "viridis",
    style="cont",
    breaks = c(0,1))+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="blue")+
  tm_layout(title = "Semi-natural areas"),

tm_shape(natOpen_slitasje_extr_trd)+
  tm_polygons(col = "w_mean",
    title="Slitasje indicator",
    palette = "viridis",
    style="cont",
    breaks = c(0,1))+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="blue")+
  tm_layout(title = "Naturally open areas"),
HIA_trd)
```

@@

> *The maps abov are easy to misunderstand, and they should therefor be
> communicated with caution. They should be considered as temporary
> files or as by-products.*

>>>>

> *ANO could harmonise better with the Naturetype data set if it included
> 7SE and 7TK for Naturally open and Semi natural ecosystem.*

@@

It appears the proportion of each circle that is made up of the dominant
ecosystem was only recorded after year 2019. In fact, the main ecosystem
was not recorded at all in 2019:
```{r}
# Hard coding name change
#unique(ano$hovedtype_250m2)[3]
ano$hovedtype_250m2[ano$hovedtype_250m2==unique(ano$hovedtype_250m2)[3]] <- "Aapen jordvassmyr"
```

@@

This rather dense figure needs to be looked at carefully. In the top row
we see that the sample size (number of polygons) varies between
ecosystems. For naturally open ecosystems many polygons are from high
infrastructure areas, not surprisingly, and there are few points for the
lowest impact class (zero such polygons in *Sørlandet* for example). We
may therefore not be able to extrapolate indicator values for Naturally
open areas in in *Sørlandet* with low levels of infrastructure.

We can also from the middle row see the association between the indicator
values (area weighted means) and the modified infrastructure index
(HIF). We should then not put too much weight on the bars were there is
little data (low n) and/or high standard error (sd, bottom row). For
example, with Naturally open ecosystems,

Midt-Norge has the overall lowest errors, and there we also see the kind of relationship between
the indicator and the pressure that we want to see (middle row). The
pattern is repeated for all regions except Østlandet, but there we also
see that HIF class 3 has very little data, and a high sd, and this could
explain the discrepancy (but it doesn't support the general relationship
either).

@@

```{r, fig.cap="Slitasje indicator extrapolated over Trondheim"}
myCol <- "RdYlGn"
tmap_arrange(
tm_shape(wetlands_slitasje_extr_trd)+
  tm_polygons(col = "w_mean",
    title="Slitasje indicator",
    palette = myCol,
    style="cont",
    breaks = c(0,1))+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="blue")+
  tm_layout(title = "Wetland"),

tm_shape(seminat_slitasje_extr_trd)+
  tm_polygons(col = "w_mean",
    title="Slitasje indicator",
    palette = myCol,
    style="cont",
    breaks = c(0,1))+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="blue")+
  tm_layout(title = "Semi-natural areas"),

tm_shape(natOpen_slitasje_extr_trd)+
  tm_polygons(col = "w_mean",
    title="Slitasje indicator",
    palette = myCol,
    style="cont",
    breaks = c(0,1))+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="blue")+
  tm_layout(title = "Naturally open areas"),
HIA_trd)
```

@@

> *The maps above are easy to misunderstand, and they should therefor be
> communicated with caution. They should be considered as temporary
> files or as by-products.*
